Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-26 writeup/gz_hubble_data.tex
updating decision tree figure with correct task numbers

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{}
\label{fig:decisiontree}
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers. Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1st tier questions which are asked of all users. Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
\label{fig:decisiontree}
\end{center}
\end{figure*}
